---
title: "Unintuitive Results"
author: "Ayush Patel"
format: html
---

This is a small reporducible document to generate some results which I find unintuituve from the `People of India` dataset of CMIE. I am using the `people_of_india_20230101_20230431.csv` file, with state and country level weights are required.

## Libraries

```{r}
library(here)
library(dplyr)
library(tidyr)

```

## load data, keep accepted responses and create weights

```{r}
people <- readr::read_csv(
  here("data","data-for-descriptive-analysis",
       "people_of_india_20230101_20230430_R.csv")
)

## Keep only accepted responses from the 'people' data

people|>
  filter(RESPONSE_STATUS == "Accepted")|>
  mutate(
    uid = paste(HH_ID,MEM_ID,sep = "")
  )-> people

## create weights

people|>
  mutate(
    w_state = MEM_WEIGHT_FOR_STATE_W *
      MEM_NON_RESPONSE_FOR_STATE_W,
    w_country = MEM_WEIGHT_FOR_COUNTRY_W *
      MEM_NON_RESPONSE_FOR_COUNTRY_W
  ) -> people
```

## define target group

```{r}
# Since there is no way to know if a person has a 
# written contract or gets paid leave, the only
# reasonable variable we are left with is people
# having a PF account. We can try using nature of
# occupation along with PF.

### let us see, from those who are employed and looking
### for a job have a pf account in india and maharashtra.
### This will give us uid foe target group.

people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|> 
  filter(NATURE_OF_OCCUPATION %in% c(
    "Wage Labourer",
    "Industrial Workers",
    "Non-Industrial Technical Employee",
    "Small Trader/Hawker/ Businessman without Fixed Premises",
    "Home-based Worker",
    "Self Employed Entrepreneur",
    "Support Staff",
    "White Collar Clerical Employees"
  ))|>
  filter(OCCUPATION != "Smaller businessmen (smaller shops or offices), Shopkeepers, small dhaba owners")|>
  filter(HAS_PF_AC == "N")|>
  filter(EMPLOYMENT_STATUS %in% c("Employed",
                                  "Unemployed, willing and looking for a job",
                                  "Unemployed, willing but not looking for a job"))|>
  pull(uid) -> uid_target_group_without_homemaker_student

people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|> 
  filter(NATURE_OF_OCCUPATION %in% c(
    "Wage Labourer",
    "Industrial Workers",
    "Non-Industrial Technical Employee",
    "Small Trader/Hawker/ Businessman without Fixed Premises",
    "Home-based Worker",
    "Self Employed Entrepreneur",
    "Support Staff",
    "White Collar Clerical Employees",
    "Student",
    "Home Maker"
  ))|>
  filter(OCCUPATION != "Smaller businessmen (smaller shops or offices), Shopkeepers, small dhaba owners")|>
  filter(HAS_PF_AC == "N")|>
  filter(EMPLOYMENT_STATUS %in% c("Employed",
                                  "Unemployed, willing and looking for a job",
                                  "Unemployed, willing but not looking for a job"))|>
  pull(uid) -> uid_target_group_with_homemaker_student

people|>
  filter(uid %in% uid_target_group_without_homemaker_student)|>
  pull(HH_ID)|>
  unique() -> hhid_target_group_without_homemaker_student

people|>
  filter(uid %in% uid_target_group_with_homemaker_student)|>
  pull(HH_ID)|>
  unique() -> hhid_target_group_with_homemaker_student


people|>
  mutate(
    is_tg = ifelse(
      uid %in% uid_target_group_without_homemaker_student,
      1,0
    ),
    is_tg_plus_stu_hm = ifelse(
      uid %in% uid_target_group_with_homemaker_student,
      1,
      0
    )
  )-> people

```

## Reasonable estimates

**Population of India**

```{r}
people|>
  pull(w_country)|>
  sum()
```

**Population of Maharashtra**

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  pull(w_state)|>
  sum()
```

**Percentage of people (above15) in India with Bank Accounts**

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  summarise(
    perc_has_bank_ac = DescTools::Mean(
      ifelse(HAS_BANK_AC == "Y",
             1,0),
      weights = w_country
    )
  )
```

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(REGION_TYPE)|>
  summarise(
    perc_has_bank_ac = DescTools::Mean(
      ifelse(HAS_BANK_AC == "Y",
             1,0),
      weights = w_country
    )
  )
```
**Percentage of people (above15) in Maharashtra with Bank Accounts**

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  summarise(
    perc_has_bank_ac = DescTools::Mean(
      ifelse(HAS_BANK_AC == "Y",
             1,0),
      weights = w_state
    )
  )
```

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(REGION_TYPE)|>
  summarise(
    perc_has_bank_ac = DescTools::Mean(
      ifelse(HAS_BANK_AC == "Y",
             1,0),
      weights = w_state
    )
  )
```

## The unintuitive result

Mostly it to do with if a member has a mobile.

**Percentage of people(above15) in India with a mobile**

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE == "Y",
             1,0),
      weights = w_country
    )
  )
```

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(REGION_TYPE)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE== "Y",
             1,0),
      weights = w_country
    )
  )
```
> The above two results are not too alarming, see what happens when we see below for people in target group vs people not in target group.

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE == "Y",
             1,0),
      weights = w_country
    )
  )
```

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg,REGION_TYPE)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE== "Y",
             1,0),
      weights = w_country
    )
  )
```
> This is the real brain teaser to me, **%people in target group that have mobile is higher than %people not in target with mobile. This result follows for India and most states **

**Percentage of people(above15) in Maharashtra with a mobile**

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE == "Y",
             1,0),
      weights = w_state
    )
  )
```

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(REGION_TYPE)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE== "Y",
             1,0),
      weights = w_state
    )
  )
```


```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE == "Y",
             1,0),
      weights = w_state
    )
  )
```

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg,REGION_TYPE)|>
  summarise(
    perc_has_mobile = DescTools::Mean(
      ifelse(HAS_MOBILE== "Y",
             1,0),
      weights = w_state
    )
  )
```

## Results where target group numbers seem high

**Percentage of people in India(above15) in tg vs not in tg that have life insurance**

```{r}
people|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg)|>
  summarise(
    perc_has_lic = DescTools::Mean(
      ifelse(HAS_LIC== "Y",
             1,0),
      weights = w_country
    )
  )
  
```

**Percentage of people in Maharashtra(above15) in tg vs not in tg that have life insurance**

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg)|>
  summarise(
    perc_has_lic = DescTools::Mean(
      ifelse(HAS_LIC== "Y",
             1,0),
      weights = w_state
    )
  )
  
```

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg, REGION_TYPE)|>
  summarise(
    perc_has_lic = DescTools::Mean(
      ifelse(HAS_LIC== "Y",
             1,0),
      weights = w_state
    )
  )
  
```

**Same issue with health insurance**

```{r}
people|>
  filter(STATE == "Maharashtra")|>
  filter(AGE_YRS>15 | 
           (AGE_YRS ==15 & AGE_MTHS >0))|>
  group_by(is_tg, REGION_TYPE)|>
  summarise(
    perc_has_health_ins = DescTools::Mean(
      ifelse(HAS_HEALTH_INSURANCE== "Y",
             1,0),
      weights = w_state
    )
  )
  
```